### 2015-07-06 narrative/data-description.tex
Polishing data description section

The data description may be stored with the individual chunks or within a
seprate metadata service or both to aid QoS requirements. It would contain
conventional attributes such as data type, size, dimensionality, and the
relationship to other data. In particular, the relationship to other chunks can
be captured by including \textit{typed links} each representing a different
relationship type.  In this project, a key metric stored as a metadata
attribute is \textit{data utility}.  It enables QoS scheduling, data placement
decisions, data lifetime decisions, and captures the chunk priority. It is
our belief that exascale science will require users to prioritize a small set
of chunks to be saved on higher-level capacity-limited storage to avoid the
slow access to large-capacity lower-level storage, such as tape.  We propose a
new technique, described by a utility function provided by a user, where chunks
can be cast into multiple data buckets and each bucket can be prioritized
differently according to its utility value.  Once this is done, the middleware
system will construct the data description and re-organize and place data to
achieve the desired QoS goals and policies.

In the meanwhile, the user would like a certain Quality of Service such that
they can then make decisions about what data to access when.
%for example is less than what they desire and will then place in a certain set
%of rules which the system can make autonomic decisions to help decide what
%should be done.
A key insight in this proposed project has been the increased interaction of
the application with the storage system. Towards this end, we propose to
address the QoS requirements by providing the application with mechanisms to
specify the quality of I/O service, interrogate the storage system, and react
to the responses. Guided by our past work we propose to explore the design of
mechanisms for this purpose.

>>>>

The data description may be stored with the individual chunks or within a
separate metadata service or both to aid QoS requirements. It would contain
conventional attributes such as data type, size, dimensionality, and the
relationship to other data. In particular, the relationship to other chunks can
be captured by including \textit{typed links} each representing a different
relationship type.  In this project, a key metric stored as a metadata
attribute is \textit{data utility}.  It enables QoS scheduling, data placement
decisions, data lifetime decisions, and captures the chunk priority. It is
our belief that exascale science will require users to prioritize a small set
of chunks to be saved on higher-level capacity-limited storage to avoid the
slow access to large-capacity lower-level storage, such as tape.  We propose a
new technique, described by a utility function provided by a user, where chunks
can be cast into multiple data buckets and each bucket can be prioritized
differently according to its utility value.  Once this is done, the middleware
system will construct the data description and re-organize and place data to
achieve the desired QoS goals and policies.

A key insight in this proposed project has been the increased interaction of
the application with the storage system.
The user would like to have the ability to obtain information about, and even
negotiate with the system to determin what
level of Quality of Service is possible given
a prospective set of I/O operations and current state of the system, so that
they can then make decisions about what data to access when.
%for example is less than what they desire and will then place in a certain set
%of rules which the system can make autonomic decisions to help decide what
%should be done.
Towards this end, we propose to
address the QoS requirements by providing the application with mechanisms to
specify the quality of I/O service, interrogate the storage system, and react
to the responses. Guided by our past work we propose to explore the design of
mechanisms for this purpose.
